---
title: "Prediction Summaries"
author: "Shannon E. Ellis"
output: 
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{recount quick start guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
## Track time spent on making the vignette
startTime <- Sys.time()
```

```{r load-packages, echo=FALSE, message = FALSE, warning = FALSE}
## load libraries
library(tidyverse)
library(caret)
library(reshape)
library(xtable)

## Set colors
## import colors to use
bright= c(red=rgb(222,45,38, maxColorValue=255), #de2d26
        pink=rgb( 255, 102, 153, maxColorValue=255), #ff6699
        orange=rgb(232,121,12, maxColorValue=255),   #e8790c
        yellow=rgb(255,222,13, maxColorValue=255), #ffde0d          
        green=rgb(12,189,24, maxColorValue=255),  #0cbd18           
        teal=rgb(59,196,199, maxColorValue=255), #3bc4c7
        blue=rgb(58,158,234, maxColorValue=255), #3a9eea
        purple=rgb(148,12,232, maxColorValue=255)) #940ce8  

## load colors for when we need more than what is in bright
load("/dcl01/leek/data/sellis/barcoding/plots/colors31.rda")
colors31 = as.character(colors31)
```

```{r load-data, echo=FALSE, message=FALSE, warning = FALSE}
## load predictedicted phenotypes
load('/dcl01/leek/data/sellis/barcoding/output/PredictedPhenotypes_v0.0.06.rda')
df = PredictedPhenotypes #70479
## 70479

## load SRA metadata
### Load in SRA metadata
load('/dcl01/leek/data/recount-website/metadata/metadata_sra.Rdata')
metadata <- metadata[!is.na(metadata$bigwig_path), ]
sra_meta = metadata
rm(metadata)
### Keep only the good SRA and get them in the same order
pd = read_csv("https://raw.githubusercontent.com/nellore/runs/master/sra/v2/hg38/SraRunInfo.csv")
sra_meta = left_join(as.data.frame(sra_meta),pd,by=c("run"="Run","sample"="Sample"))

## GTEx metadata
load("/dcl01/leek/data/sellis/barcoding/data/rda/gtexmetadata.rda")
gtex_meta = gtexmetadata
gtex_meta = cbind(gtex_meta,usegtex)
rm(gtexmetadata,usegtex)
gtex_meta[is.na(gtex_meta[,"SMTS"]),"SMTS"] <- c("Esophagus","Skin","Stomach","Skin","Esophagus")
usegtex = gtex_meta$usegtex
pheno = gtex_meta
gtex_meta = pheno[usegtex,]

## TCGA metadata
# get phenotype info in order
recount::all_metadata('TCGA') -> md 
```


# Summary: recount2 

A big picture summary of the data included in recount including:

* number of samples from each data source (GTEx, SRA, and TCGA)
* distribution of the number of samples per SRA project  

```{r 'overview', message = FALSE, echo = FALSE, warning = FALSE}
## number of samples from data source
dataset_summ <- df %>%  group_by(dataset) %>% select(dataset) %>% summarise(Count = n())

## Data set sample size
ggplot(data = dataset_summ, aes(x=dataset, y = Count,label = Count)) + 
	labs(y="No. of Samples",x="Data Set",title="Sample Summary") +
    geom_bar(stat="identity", aes(fill = dataset),position="dodge") +
    geom_text(size = 6, position = position_stack(),colour="black") +
    scale_fill_manual(values=c("#940CE8", "#FF6699", "#3BC4C7"))+
    theme_bw()+
    theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5),text = element_text(size=20), panel.border = element_blank(), panel.grid.major = element_blank(),
		panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black"))

## number of projects (in SRA)
length(unique(sra_meta$project))
proj_summ <- sra_meta %>%  group_by(project) %>% select(project) %>% summarise(Count = n())

## summary of number of samples per project
ggplot(data = proj_summ, aes(Count)) + 
	labs(y="Count",x="Samples per Project",title="Number of Samples by SRA Project") +
    geom_histogram(binwidth=40)+
    theme_bw()+
    theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5),text = element_text(size=20), panel.border = element_blank(), panel.grid.major = element_blank(),
		panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black"))
```

```{r 'confusion_matrix_analysis', echo=FALSE, message = FALSE, warning = FALSE}
phenotypes = c("sex","tissue","samplesource","sequencingstrategy")

## clean up reported sex variable a little bit
  ## only compare between those annotated in SRA 
  df$reported_sex[df$reported_sex=="Female"] <- "female"
  df$reported_sex[df$reported_sex=="F"] <- "female"
  df$reported_sex[df$reported_sex=="Male"] <- "male"
  df$reported_sex[df$reported_sex=="M"] <- "male"

   ## summarize unknowns
   unknowns = names(table(df$reported_sex))[c(17:21,23:25)]
   df$reported_sex[df$reported_sex %in% unknowns] <- "unknown"

## sample source
for(phenot in phenotypes){

	reported <- df[,paste0("reported_",phenot)]
	predicted <- df[,paste0("predicted_",phenot)]

## remove samples whose reported sex only existed in <=2 samples
	if(phenot=="sex"){
		a <- table(reported)
		rownames(a[a<=2]) -> remove
		toremove <- reported %in% remove

		reported <- reported[!toremove]
		predicted <- predicted[!toremove]

		reported <- droplevels(reported)
		predicted <- droplevels(predicted)
	}
	## for tissue, remove sample whose reported is NA
	if(phenot=="tissue"){
		remove <- (reported=="NA" | is.na(reported))

		reported <- reported[!remove]
		predicted <- predicted[!remove]

		xtab_tissue_all <- table(predicted,reported)

		keep <- reported %in% names(table(predicted))
		reported <- reported[keep]
		predicted <- predicted[keep]

		reported <- droplevels(reported)
		predicted <- droplevels(predicted)
		levels(reported) <- levels(predicted)

 		tiss<-bind_cols(reported=reported,predicted=predicted)
	}
	
	xtab <- table(predicted,reported)
	assign(paste0("xtab_",phenot),xtab)
	
	if(phenot=="sex" | phenot=="tissue"){
		 levels(predicted) <- levels(reported)
	}else{
		levels(reported) <- levels(predicted)
	}


	conf <- confusionMatrix(predicted,reported)	
	assign(paste0("conf_",phenot),conf)

	# Sensitivity= true positives/(true positive + false negative)
	# Specificity=true negatives/(true negative + false positives)

	DF <- as.data.frame(xtab)
	predicteds <- unique(DF$predicted)
	Vals = matrix(NA,ncol=nrow(xtab),nrow=2)
	rownames(Vals) <- c("Sensitivity", "Specificity")
	colnames(Vals) <- paste0(phenot,"_",predicteds)

	for(lab in predicteds){
		TP <- DF %>% dplyr::filter(predicted==lab, reported==lab) %>% select(Freq)%>% colSums()
		FP <- DF %>% dplyr::filter(predicted==lab, reported!=lab) %>% select(Freq) %>% colSums()
		TN <- DF %>% dplyr::filter(predicted!=lab, reported!=lab) %>% select(Freq)%>% colSums()
		FN <- DF %>% dplyr::filter(predicted!=lab, reported==lab) %>% select(Freq)%>% colSums()

		Vals[1,paste0(phenot,"_",lab)] <- TP/(TP+FN)
		Vals[2,paste0(phenot,"_",lab)] <- TN/(TN+FP)
	}	
	assign(paste0("Vals_",phenot),Vals)
}

Vals_all<-cbind(Vals_tissue,Vals_sex,Vals_sequencingstrategy,Vals_samplesource)

## sensitivity and specificity summary
# summary(na.omit(Vals_all[1,]))
# summary(na.omit(Vals_all[2,]))

# print(xtable(xtab_sex), comment=F, type="html")
# print(xtable(xtab_tissue_all), comment=F, type="html")
# print(xtable(xtab_samplesource), comment=F, type="html")
# print(xtable(xtab_sequencingstrategy), comment=F, type="html")


### let's look as a percentage
x1<-as.table(apply(xtab_tissue,1,prop.table))
x2<-as.table(apply(xtab_sex,1,prop.table))
x3<-as.table(apply(xtab_samplesource,1,prop.table))
x4<-as.table(apply(xtab_sequencingstrategy,1,prop.table))

#Sensitivity and Specificity

sens_tissue<-t(Vals_tissue) %>% melt() %>% mutate(category=gsub("tissue_","",X1))
sens_sex<-t(Vals_sex) %>% melt() %>% mutate(category=gsub("sex_","",X1))
sens_sequencingstrategy<-t(Vals_sequencingstrategy) %>% melt() %>% mutate(category=gsub("sequencingstrategy_","",X1))
sens_samplesource<-t(Vals_samplesource) %>% melt() %>% mutate(category=gsub("samplesource_","",X1))
```

# Sex

A summary of sex across recount including:

* overall breakdown of predicted sex across recount
* breakdown of predicted sex within SRA data
* Comparison of reported sex to predicted sex (frequency)
* Comparison of reported sex to predicted sex (proportion)
* specificity and sensitivity for sex
* Confusion Matrix for reported to prediced sex agreement (proportion)

```{r 'sex', message = FALSE, warning = FALSE, echo = FALSE, fig.width = 8, fig.height = 8, results="asis"}
a<-df %>% select(predicted_sex) %>% table() %>% melt()
colnames(a) <- c("predicted","Count")
a

ggplot(as.data.frame(a), aes(x=predicted, y = Count)) + 
	geom_bar(stat="identity")+
	labs(x="Predicted Sex")+
	scale_fill_manual("black")+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

 ## Sex breakdown within SRA
(sex_SRA <- df %>% dplyr::filter(dataset=="sra") %>%  group_by(predicted_sex) %>% select(predicted_sex) %>% summarise(Count = n())) 

ggplot(data = sex_SRA, aes(x=predicted_sex, y = Count,label = Count)) + 
	labs(y="No. of Samples",x="Data Set",title="Predicted Sex") +
    geom_bar(stat="identity", aes(fill = predicted_sex),position="dodge") +
    geom_text(aes(fill=predicted_sex),size = 12, position = position_dodge(width = 0.9),colour="black") +
    scale_fill_manual(values=c("#940CE8", "#0CBD18", "grey48"))+
    theme_bw()+
    theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5),text = element_text(size=14), panel.border = element_blank(), panel.grid.major = element_blank(),
		panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black"))

print(xtable(t(Vals_sex)), comment=F, type="html")

ggplot(sens_sex, aes(x=category, y = value, fill=X2)) + 
	geom_bar(stat="identity",position="dodge")+
	labs(x="",y="",title="Sex")+
	scale_fill_manual(values=c("#940CE8","#E8790C"))+
	theme_bw()+
  	theme(legend.title=element_blank(), plot.title = element_text(size=16,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

 print(xtable(xtab_sex), comment=F, type="html")

 ggplot(as.data.frame(xtab_sex), aes(x=predicted, y = Freq, fill=reported)) + 
	geom_bar(stat="identity")+
	labs(title="Sex")+
	scale_fill_manual(values=c("#FF6699", "#FFDE0D","#3A9EEA","#940CE8","#0CBD18","#DE2D26","#3BC4C7","#E8790C", "gray84"))+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black", size=16))


	colors2 = c("#FF6699", "#FFDE0D","#3A9EEA","#940CE8","#0CBD18","#DE2D26","#3BC4C7","#E8790C", "gray84")
	labl <- "Sex"
	right <- 7
	left <- max(colSums(x2))
	nc=1
	par(mar=c(6.1, 4.1, 4.1, 15.1))

	barplot(x2, 
		# beside=T,
		col=colors2, 
		las=2,
		legend.text=TRUE,
		cex.axis=1,
		cex.main = 2,
		cex.lab = 1,
		cex.names=1,
		main=labl,
		ylab="proportion",
		# xlab= "predicted",
	    args.legend=list(
	      x=right,
	      y=left,
	      cex=1.2,
	      ncol=nc,
	      bty = "n"
	    )
	)

ggplot(data = as.data.frame(x2), aes(x=predicted, y=reported, fill=Freq)) + 
  geom_tile()+
  theme(legend.title=element_blank(),text = element_text(size=14),plot.title = element_text(size=20,hjust = 0.5),axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Sex")


```

# Tissue 

A summary of tissue across recount including:

* overall breakdown of predicted tissue across recount
* overall breakdown of concordance between predicted and reported tissue 
* specific breakdown of concordance between predicted and reported tissue (frequency)
* specific breakdown of concordance between predicted and reported tissue (proportion)
* specificity and sensitivity for tissue
* Confusion Matrix for reported to prediced tissue agreement (proportion)

```{r 'tissue', message = FALSE, warning = FALSE, echo = FALSE, fig.width = 8, fig.height = 8, results="asis"}

## overall breakdown of predicted tissue
a<- df %>% select(predicted_tissue) %>% table() %>% melt()
colnames(a) <- c("predicted_tissue","Count")
a 

ggplot(as.data.frame(a), aes(x=predicted_tissue, y = Count)) + 
	geom_bar(stat="identity")+
	labs(x="Predicted Tissue")+
	scale_fill_manual("black")+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))


## samples discordant or concordant for tissue
a<- tiss %>% mutate(new=(as.character(predicted)==as.character(reported)))
a$new[a$new=="TRUE"] <- "concordant"
a$new[a$new=="FALSE"] <- "discordant"
a <- a %>% group_by(new) %>% dplyr::count(predicted,new)

ggplot(as.data.frame(a), aes(x=predicted, y = n, fill=new)) + 
	geom_bar(stat="identity")+
	labs(x="Predicted Tissue",y="Count")+
	scale_fill_manual(values=c("black","gray48"))+
	theme_bw()+
  	theme(legend.title=element_blank(),plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

print(xtable(t(Vals_tissue)), comment=F, type="html")

ggplot(sens_tissue, aes(x=category, y = value, fill=X2)) + 
	geom_bar(stat="identity",position="dodge")+
	labs(x="",y="",title="Tissue")+
	scale_fill_manual(values=c("#940CE8","#E8790C"))+
	theme_bw()+
  	theme(legend.title=element_blank(), plot.title = element_text(size=16,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))


## barplot colored by mismatch
b <- xtab_tissue[,dimnames(xtab_tissue)$reported %in% dimnames(xtab_tissue)$predicted]  	
  	ggplot(as.data.frame(b), aes(x=predicted, y = Freq, fill=reported)) + 
	geom_bar(stat="identity")+
	labs(title="Tissue")+
	scale_fill_manual(values=colors31)+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=12), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=12))
#
# barplot colored by mismatch (proportion)
  		colors2 = colors31
		labl <- "Tissue"
		right <- 73
		left <- 1
		nc = 2
	par(mar=c(8.1, 4.1, 4.1, 18.1))

b <- x1[dimnames(x1)$reported %in% dimnames(x1)$predicted,]  	

  	barplot(b, 
		col=colors2, 
		las=2,
		legend.text=TRUE,
		cex.axis=1,
		cex.main = 2,
		cex.lab = 1,
		cex.names=1,
		main=labl,
		ylab="proportion",
		# xlab= "predicted",
	    args.legend=list(
	      x=right,
	      y=left,
	      cex=1,
	      ncol=nc,
	      bty = "n"
	    )
	)

  ggplot(data = as.data.frame(b), aes(x=predicted, y=reported, fill=Freq)) + 
  geom_tile()+
  theme(legend.title=element_blank(),text = element_text(size=14),plot.title = element_text(size=24,hjust = 0.5),axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Tissue")

print(xtable(xtab_tissue_all), comment=F, type="html")

dimnames(xtab_tissue_all)$reported[42] <- "Cutaneous or Subcutaneous Tissue"
## confusion matrix for all reported tissues, not just the ones we had the chance to get right
  ggplot(data = as.data.frame(xtab_tissue_all), aes(x=predicted, y=reported, fill=Freq)) + 
  geom_tile()+
  theme(legend.title=element_blank(),text = element_text(size=14),plot.title = element_text(size=24,hjust = 0.5),axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Tissue")

```

# Sequencing Strategy 

A summary of sequencing strategy across recount including:

* overall breakdown of predicted sequencing strategy across recount
* breakdown of concordance between predicted and reported sequencing strategy (frequency)
* breakdown of concordance between predicted and reported sequencing strategy (proportion)
* specificity and sensitivity for sequencing strategy
* confusion Matrix for reported to prediced sequencing strategy agreement (proportion)


```{r 'sequencingstrategy', message = FALSE, warning = FALSE, echo = FALSE, fig.width = 8, fig.height = 8, results="asis"}
a<-df %>% select(predicted_sequencingstrategy) %>% table() %>% melt()
colnames(a) <- c("predicted","Count")
a 

ggplot(as.data.frame(a), aes(x=predicted, y = Count)) + 
	geom_bar(stat="identity")+
	labs(x="Predicted Sequencing Strategy")+
	scale_fill_manual("black")+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

print(xtable(t(Vals_sequencingstrategy)), comment=F, type="html")

ggplot(sens_sequencingstrategy, aes(x=category, y = value, fill=X2)) + 
	geom_bar(stat="identity",position="dodge")+
	labs(x="",y="",title="Sequencing Strategy")+
	scale_fill_manual(values=c("#940CE8","#E8790C"))+
	theme_bw()+
  	theme(legend.title=element_blank(), plot.title = element_text(size=16,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

print(xtable(xtab_sequencingstrategy), comment=F, type="html")

 ggplot(as.data.frame(xtab_sequencingstrategy), aes(x=predicted, y = Freq, fill=reported)) + geom_bar(stat="identity")+
	labs(title="Sequencing Strategy")+
	scale_fill_manual(values=c("#3A9EEA", "#E8790C", "gray84"))+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black", size=16))


	colors2 = c("#3A9EEA", "#E8790C")
	labl <- "Sequencing Strategy"
	right <- 4.7
	left <- max(colSums(x1))
	nc=1
	par(mar=c(6.1, 4.1, 4.1, 8.1))
	barplot(x4, 
		# beside=T,
		col=colors2, 
		las=2,
		legend.text=TRUE,
		cex.axis=1,
		cex.main = 2,
		cex.lab = 1,
		cex.names=1,
		main=labl,
		ylab="proportion",
		# xlab= "predicted",
	    args.legend=list(
	      x=right,
	      y=left,
	      cex=1.5,
	      ncol=nc,
	      bty = "n"
	    )
	)

ggplot(data = as.data.frame(x4), aes(x=predicted, y=reported, fill=Freq)) + 
  geom_tile()+
  theme(legend.title=element_blank(),text = element_text(size=14),plot.title = element_text(size=20,hjust = 0.5),axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Sequencing Strategy")

```

# Sample Source 

A summary of sample source across recount including:

* overall breakdown of predicted sample source across recount
* breakdown of concordance between predicted and reported sample source (frequency)
* breakdown of concordance between predicted and reported sample source(proportion)
* specificity and sensitivity for sample source
* confusion Matrix for reported to prediced sample source agreement (proportion)


```{r 'samplesource', message = FALSE, warning = FALSE, echo = FALSE, fig.width = 8, fig.height = 8, results="asis"}

a<-df %>% select(predicted_samplesource) %>% table() %>% melt()
colnames(a) <- c("predicted","Count")
a 

ggplot(as.data.frame(a), aes(x=predicted, y = Count)) + 
	geom_bar(stat="identity")+
	labs(x="Predicted Sample Source")+
	scale_fill_manual("black")+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

 print(xtable(t(Vals_samplesource)), comment=F, type="html")


ggplot(sens_samplesource, aes(x=category, y = value, fill=X2)) + 
	geom_bar(stat="identity",position="dodge")+
	labs(x="",y="",title="Sample Source")+
	scale_fill_manual(values=c("#940CE8","#E8790C"))+
	theme_bw()+
  	theme(legend.title=element_blank(), plot.title = element_text(size=16,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_text(angle=90,hjust=1),axis.text=element_text(colour="black", size=16))

print(xtable(xtab_samplesource), comment=F, type="html")

 ggplot(as.data.frame(xtab_samplesource), aes(x=predicted, y = Freq, fill=reported)) + geom_bar(stat="identity")+
	labs(title="Sample Source")+scale_fill_manual(values=c("#FFDE0D", "#FF6699", "gray84"))+
	theme_bw()+
  	theme(plot.title = element_text(size=18,hjust = 0.5),text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),axis.text=element_text(colour="black", size=16))


	colors2 = c("#FFDE0D", "#FF6699")
	labl <- "Sample Source"
	right <- 4.7
	left <- max(colSums(x3))
	nc=1
	par(mar=c(6.1, 4.1, 4.1, 8.1))
	barplot(x3, 
		# beside=T,
		col=colors2, 
		las=2,
		legend.text=TRUE,
		cex.axis=1,
		cex.main = 2,
		cex.lab = 1,
		cex.names=1,
		main=labl,
		ylab="proportion",
		# xlab= "predicted",
	    args.legend=list(
	      x=right,
	      y=left,
	      cex=1.5,
	      ncol=nc,
	      bty = "n"
	    )
	)

ggplot(data = as.data.frame(x3), aes(x=predicted, y=reported, fill=Freq)) + 
  geom_tile()+
  theme(legend.title=element_blank(),text = element_text(size=14),plot.title = element_text(size=20,hjust = 0.5),axis.text.x=element_text(angle=90,hjust=1))+
  labs(title="Sample Source")

```

# Vignette information

```{r reproducibility}
## Time spent creating this report:
diff(c(startTime, Sys.time()))

## Date this report was generated
message(Sys.time())

## Reproducibility info
options(width = 120)
devtools::session_info()
```

Code for creating the vignette

```{r createVignette, eval=FALSE}
## Create the vignette
library('rmarkdown')
system.time(render('/dcl01/leek/data/sellis/barcoding/phenotype_vignettes/Summaries.Rmd', 'BiocStyle::html_document'))

## Extract the R code
library('knitr')
knit('/dcl01/leek/data/sellis/barcoding/phenotype_vignettes/Summaries.Rmd', tangle = TRUE)
```